AFQ-Insight

### 2019-11-22 reports/manuscript/sections/methods.tex
Fixes up various merge issues from the rebase.

For given values of $\lambda_1$ and $\lambda_2$, the cost function in equation
\ref{eq:sgl} can be optimized using proximal gradient descent methods
\cite{parikh2014proximal} here implemented as a custom proximal operator that is
then optimized using the COPT library \cite{fabian_pedregosa_2018_1473584}. To
find the values of the metaparameters $\lambda_1$ and $\lambda_2$, we used a
hyperoptimization procedure, implemented using the hyperopt software
\cite{Bergstra_2015}. XXX We need more details here.

>>>>

For given values of $\lambda_1$ and $\lambda_2$, the cost function in equation
\ref{eq:sgl} can be optimized using proximal gradient descent methods
\cite{parikh2014proximal} here implemented as a custom proximal operator that is
then optimized using the COPT library \ariel{citation needed here}. To
find the values of the metaparameters $\lambda_1$ and $\lambda_2$, we used a
hyperoptimization procedure, implemented using the hyperopt software
\cite{Bergstra_2015}. XXX We need more details here.
